---
title: "Who Represents You?"
author: "Priyanshi Rastogi"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
source("api-keys.R")
source("civic-info.R")
source("propublica.R")
```

##Your Representatives:

This is a report about the political representatives based on the address entered(). This report draws upon data from the ProPublica API (https://projects.propublica.org/api-docs/congress-api/) and the Google Civic Data API (https://developers.google.com/civic-information/). As an overview, here is a summary of _who_ represents the address given (from the **local** to the **national** level).

```{r echo = FALSE}
kable(new_df)

```

##House of Representatives:
Now let's take a look at **all** of the congressional representatives(in the
House of Representatives, _not_ the Senate) for the state in which the address was given. We see this breakdown by gender and political party for those members of the House.

```{r House of Rep chart, echo = FALSE}
propublica_gender_plot

party_plot
```

###`r member_name`
Let's learn a bit more about one representative, _`r member_name`_. The representative is `r member_age` years old, and you can find them on twitter at `r twitter_link`. Interestingly, of the last 20 congressional votes, the representative was in accordance with the majority `r agreed_percentage`% of the time.
